API design for machine learning: experiences from scikit-learn

### 2014-02-12 paper.tex
example of fit_transform's efficiency

Every transformer allows \texttt{fit(X).transform(X)}
to be written as \texttt{fit\_transform(X)}.
This combined operation prevents repeated computations,
either by skipping only an input validation step,
or by using a more efficient algorithm for the transformation.
In the same spirit, clustering algorithms provide a \texttt{fit\_predict}
that is equivalent to \texttt{fit} followed by \texttt{predict},
returning cluster labels for the training samples.

>>>>

Every transformer allows \texttt{fit(X).transform(X)}
to be written as \texttt{fit\_transform(X)}.
This combined operation prevents repeated computations,
either by skipping only an input validation step,
or by using a more efficient algorithm for the transformation.
For example, dimensionality reduction
using truncated singular value decomposition (SVD)
computes $U_k \Sigma_k V_k^\mathsf{T} \approx X$ in its \texttt{fit} phase;
its transform phase then computes $X_k = XV$,
but the combined \texttt{fit\_transform}
can compute the same result more economically as $X_k = U\Sigma^\mathsf{T}$.
In the same spirit, clustering algorithms provide a \texttt{fit\_predict}
that is equivalent to \texttt{fit} followed by \texttt{predict},
returning cluster labels for the training samples.
